% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{hyperref}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\begin{document}

\name{Akshay Agarwal\\[0pt]} % the \\[12pt] adds a blank line after name

\address{ \textbf{Phone}:\hspace{1mm}\href{+1-669-400-9729}{+1-669-400-9729}\hspace{5mm} \textbf{Github}:\hspace{1mm}\href{https://github.com/akshay-agarwal}{akshay-agarwal}\hspace{5mm}      \textbf{Email}:\hspace{1mm}\href{mailto:akshay.agwl@gmail.com}{akshay.agwl@gmail.com} }

\begin{resume}


\section{Objective }

  Seeking an internship in Software Engineering in an organization where I can con-tribute towards its growth using my technical background and experience.
  
\section{Interests}

  Full stack web development, Mobile app development and Big Data / Analytics

\section{Education}
  Masters in Software Engineering \\
  \vspace{1.5mm}
  {\bf San Jose State University}, August 2016 - May 2018(Expected Graduation) \\ 
  B.Tech. in Computer Science and Engineering \\
  {\bf GMR Institute of Technology}, 2009 - 2013 {\bf (CG 3.5/4.0) } \\
  
\section{Skill Set}
   \begin{tabular}{l p{3in}}
    {\bf Programming:} & JAVA, Python, PHP, C \\
    {\bf Databases:} &  MySQL, IBM DB2  \\
    {\bf Web Technologies:} &  HTML5, CSS 3.0, JavaScript, Node.js \\
    {\bf Cloud Technologies:} &  AWS, IBM BlueMix \\
    \bf {Dev Tools:} & Eclipse, IntelliJ, Git \\
    {\bf Testing Tools:} & Saucelabs, JIRA, Perfecto \\
    {\bf Other:} & Docker,Linux, Android, Scrum \\
     \end{tabular}

\section{Experience}

 {\bf Software Engineer,} Accenture \hfill Jan  2014  - July 2016
 \begin{itemize} \itemsep -1pt  % reduce space between items
 \item Designed and developed scripts for a new version of test architecture that boosted automation by 30 percent, imbibing scrum methodology
 \item Interfaced with stakeholders to understand functional requirements
  \item Developed UI, Visual and API end to end tests.
  \item Designed and developed test scripts Mobile/Tablet Testing of a payment app.
 \end{itemize}
 
 {\bf Software Engineer Intern,} Genpact \hfill Nov  2013  - Dec 2013
 \begin{itemize} \itemsep -1pt  % reduce space between items
 \item Designed developed maintained the dynamic web pages using HTML, CSS & javascript
 \item Contributed in all phases of SDLC from requirements gathering to maintenance
\end{itemize}
 
\section{Academic Projects}
 
 {\bf BloodLine }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed a Node.js application that tracks blood donation using 'BlockChain'.
 \item This was built on Hyperledger using IBM's Chaincode.
 \end{itemize}
 
 {\bf Mobile Sensor Cloud Infrastructure as a Service }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed a Mobile Sensor Iaas  using  AWS, PHP, MySQL, HTML, CSS.
 \item Comprised cloud components like Scalability, Load-balancing, Dashboard, \item Wrote a survey paper on Monitoring, Billing, Management and Virtualization of mobile sensor network.
 A Comprehensive Study on Mobile Sensing and Cloud Services.
 \end{itemize}
 
 {\bf Battleship(Game) }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item A rich-UI multi-player game based on binary Search using Java in Greenfoot.
 \item The team followed Scrum and Kanban practices during the development 
 \end{itemize}

 {\bf Marks Management System }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item An web application to track Marks of a student using HTML, CSS,  Bootstrap, Java Script and MySQL.
 \item Can be used by students, teachers and parents.
 \end{itemize}
 
 \section{Hobby Projects}
 
 {\bf Twitter Clone Application }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Built a FullStack twitter clone application project.
 \item Created the web server using Node.js and Java Script.
  \item Developed the front end using HTML & CSS and used MySQL as the database.
 \end{itemize}
 
 {\bf Google Home Voice Control }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Built a smart home application using Google home and Raspberry Pi.
 \item Google home will perform voice commands from user & perform actions.
 \end{itemize}
 
\section{Other}
 Accenture All India level Delivery Week Technology Quiz Champion, 2015.\\
 Volunteer at Silicon Valley Code Camp & ISO-SJSU.\\
 Regularly solving data structures problems at leetcode. \\

\end{resume}
\end{document}